---
title: "Tips & Tricks"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here's a list of a few extra issues you might run into while writing your thesis, and some potential solutions. Most of this is based on my own experience, so your mileage may vary. If I hear of any additional bottlenecks I'd be happy to include them.

## Microsoft Word

While writing the thesis, you might want to output it to a `.docx` file, say if your supervisors prefer to work with Microsoft Word instead. This is possible, although not all `bookdown` / RMarkdown features are supported. It will get you most of the way there, but you might have to edit the Word file a bit, or inform your supervisors that this is not exactly what the final version will look like.

To render the whole thesis to one Word file, run the following:

```{r eval=FALSE}
bookdown::render_book("index.Rmd", output_format = "bookdown::word_document2")
```

You can also render a single chapter (e.g. if you want to send it out for feedback):

```{r eval=FALSE}
# render chapter 2 to Word
bookdown::preview_chapter("02-chapter.Rmd", output_format = "bookdown::word_document2")
```

In both cases, you should now find a `thesis.docx` file in the output folder (`/_book/`) by default.

* Using Python
* Switching languages
* Citation styles (pandoc + CSL, latex)
* `knitr::is_html_output()` & `knitr::is_latex_output()`
* figures: `knitr::include_graphics(auto_pdf = TRUE)`
* publishing the website
* table packages (kable, kableExtra, papaja)
* float positions
* inline code
* `\chaptermark{}` for long headers
